Global case

### 2025-05-06 lipschitz/Lipitschz.tex
update

	The vector $\hat{\boldsymbol{z}}$ is called post-activation values, 
	$\boldsymbol{z}$ is called pre-activation values, 
	and $\boldsymbol{z}^{i}_j$ is used to call the $j$-th neuron in the $i$-th layer. 
	For $\boldsymbol{x}=\vz^0$ the (vector of) input, we denote by $f(\boldsymbol{x})=\vz^\ell$ the output. Finally, pre- and post-activation neurons are called \emph{nodes}, and when we refer to a specific node/neuron, we use $a,b,c,d,n$ to denote them, and $W_{a,b} \in \mathbb{R}$ to denote the weight from neuron $a$ to $b$. Similarly, for input $\boldsymbol{x}$, we denote by $\val_{\boldsymbol{x}}(a)$ the value of neuron $a$ when the input is $\boldsymbol{x}$.

	For convenience, we write $n < z$ if neuron $n$ is on a layer before $\ell_z$, and $n \leq z$ if $n< z$ or $n=z$.

	%Concerning the verification problem, we focus on the well studied local-robustness question. Local robustness asks to determine whether the output of a neural network will be affected under small perturbations to the input. 
	%Formally, for an input $\vx$ perturbed by $\varepsilon >0$ under distance $d$, then the DNN is locally $\varepsilon$-robust in $\vx$ whenever:
	%\begin{align*}
	%	\forall \boldsymbol{x'} \text{ s.t. } d(\vx,\vx')\leq \varepsilon, \text{ we have }  
	%	argmax_i (f(\boldsymbol{x'})[i]) = argmax_i(f(\boldsymbol{x})[i])
	%\end{align*}

>>>>

	The vector $\hat{\boldsymbol{z}}$ is called post-activation values, 
	$\boldsymbol{z}$ is called pre-activation values, 
	and $\boldsymbol{z}^{i}_j$ is used to call the $j$-th neuron in the $i$-th layer. 
	For $\boldsymbol{x}=\vz^0$ the (vector of) input, we denote by $f(\boldsymbol{x})=\vz^\ell$ the output. Finally, pre- and post-activation neurons are called \emph{nodes}, and when we refer to a specific node/neuron, we use $a,b,c,d,n$ to denote them, and $W_{a,b} \in \mathbb{R}$ to denote the weight from neuron $a$ to $b$. Similarly, for input $\boldsymbol{x}$, we denote by $\val_{\boldsymbol{x}}(a)$ the value of neuron $a$ when the input is $\boldsymbol{x}$.	For convenience, we write $n < z$ if neuron $n$ is on a layer before $\ell_z$, and $n \leq z$ if $n< z$ or $n=z$.

	Concerning the verification problem, we focus on the global-robustness question. Global robustness asks to determine how the output of a neural network will be affected under a certain kind of small perturbations to any possible input. In this view, Lipschitz continuity is a good characterization of global robustness.

	Recall the definition of Lipschitz continuity:
	 under distance $d$, a function $f(x)$ is Lipschitz continuous with respect to constant $K$ if:
	\begin{align*}
		\forall \boldsymbol{x} \forall\boldsymbol{y} (|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K|\boldsymbol{x}-\boldsymbol{y}|)
	\end{align*}

	In our practice of global robustness, we will consider the following weaker property with respect to a certain number $\epsilon$:

	\begin{align*}
		\forall \boldsymbol{x} \forall\boldsymbol{y} &  (|\boldsymbol{x}-\boldsymbol{y}| \geq \epsilon \implies|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K|\boldsymbol{x}-\boldsymbol{y}|\\
		&  |\boldsymbol{x}-\boldsymbol{y}| < \epsilon \implies|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K\epsilon)
	\end{align*}
